Linearly Ordered Attribute Grammar scheduling using SAT-solving

### 2015-01-16 paper/paper.tex
Tabel

\begin{table}
  \begin{center}
    \begin{tabular}{l || c || r}
      Algorithm   &   Manual annotations   &  Compile time MainAG \\
      \hline
      Kastens'                &   Y           &   17s \\
      Kennedy-Warren  &   N           &   33s \\
      LOAG-backtrack  &   N           &   13s \\
      LOAG-SAT           &   N           &   9s \\
    \end{tabular}
  \end{center}
  \caption{Comparison of the four scheduling algorithms}
  \label{tab:algo-comparison}
\end{table}

>>>>

\begin{table}
  \begin{center}
    \begin{tabular}{l || c || r || r || r || r}
      Algorithm   &   Kastens' & Kennedy-Warren & LOAG-backtrack & LOAG-SAT\\
      \hline
      UHC's MainAG          &   -       & 33s   & 13s   & 9s    \\
      Asil Test             &   -       & 1.8s  & 4.4s  & 3.4s  \\
      Asil ByteCode         &   -       & 0.6s  & 29.4s & 2.8s  \\
      Asil PrettyTree       &   -       & 390ms & 536ms & 585ms \\
      Asil InsertLabels     &   -       & 314ms & 440ms & 452ms \\
      UUAGC's CodeGeneration&   -       & 348ms & 580ms & 382ms \\
      5 pigeonholes         &   -       & 107ms & 1970ms& 191ms \\ 
      Helium's TS\_Analyse  &   190ms   & 226ms & 235ms & 278ms \\
    \end{tabular}
  \end{center}
  \caption{Comparison of the four scheduling algorithms}
  \label{tab:algo-comparison}
\end{table}
